Testing the Relationship between Phenomenological Control related to Illusion Sensitivity

### 2025-03-19 paper/R1/manuscript.qmd
Minor changes to PCS table

::: {tbl-table2}
```{r}
suggestion <- c("Hand Lowering", "Moving Hands Together", "Mosquito Hallucination", "Taste Hallucination", "Arm Rigidity", "Arm Immobilization", "Music Hallucination", "Negative Visual Illusion", "Amnesia", "Button Press")

@@

## study design table
pcs_table <- flextable::flextable(pcs_df)
pcs_table <- set_table_properties(pcs_table, width = 1, layout = "autofit")
pcs_table <- set_caption(pcs_table, caption = "PCS Stimuli Table")
# pcs_table <- bold(study_design_table, j = "question", bold = TRUE, part = "body")
pcs_table <- theme_apa(pcs_table)

@@

:::

@@

::: {#tbl-table2}

>>>>

::: {#tbl-table2}
```{r}
suggestion <- c("Hand Lowering", "Moving Hands Together", "Mosquito Hallucination", "Taste Hallucination", "Arm Rigidity", "Arm Immobilization", "Music Hallucination", "Negative Visual Illusion", "Amnesia", "Button Press")

@@

## study design table
pcs_table <- flextable::flextable(pcs_df)
pcs_table <- set_table_properties(pcs_table, width = 1, layout = "autofit")
pcs_table <- set_caption(pcs_table, caption = "PCS Stimuli Table")
pcs_table <- set_header_labels(pcs_table, suggestion = "Suggestion", example = "Example Stimuli", question = "Task Item(s)")
pcs_table <- theme_apa(pcs_table)

@@

PCS Stimuli and Task Items
:::

@@

::: {#tbl-table3}
